Visual proteomics using whole-lamella 2D template matching

### 2022-02-20 manuscript.tex
Update word template [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/27bee68862078e46176d358694eaaf9f82467d4e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/27bee68862078e46176d358694eaaf9f82467d4e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1873152767

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/56181559e858af0a515082cd5c28c9f1b8501873/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/56181559e858af0a515082cd5c28c9f1b8501873}{jojoelfe/deco\_lace\_template\_matching\_manuscript@5618155}
on February 20, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/27bee68862078e46176d358694eaaf9f82467d4e/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/27bee68862078e46176d358694eaaf9f82467d4e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@27bee68}
on February 20, 2022.
